\input{E:/git/calben/latex-sleek-templates/letter/sleek-invoice.tex}

\address{}
\signature{Calem J Bendell}
\date{\today}

\begin{document}
	
  \begin{letter}{}
    
    The following is an estimated budget for the automation team for Solar Decathlon.
    
    In order to reach the below values we assume the house has one bedroom, one bathroom, one main room, and a kitchen attached to the main room.
    We assume prototypes pricing which may reduce with slimmer final products.
    
    Right now data collection is carried out through existing technologies, namely the Raspberry Pi and Arduino.
    Sensorica and Equipmind are working on newer, slimmer technologies designed specifically for home automation with this project in mind.
    
    I've allocated unknown expenses, such as audio collection, to be 1000 CAD.
    
    Regarding flexibility, right now 3 Raspberry Pi's are devoted to the Bedroom and 2 to the kitchen and 6 to the main room.
    Costs can be cut considerably by removing some of these units, which will include removing cameras and sensors, but this may limit the capabilities of the home.
    The humidity and temperature sensors can be similarly reduced.
    
    \begin{invoice}{CAD}{0}
      \ProjectTitle{\sffamily Report of Preliminary Budget Estimation}
      \Fee{Raspberry Pi Units Mainroom} {115} {6}
      \Fee{Raspberry Pi Units Bedroom} {115} {3}
      \Fee{Raspberry Pi Units Kitchen} {115} {2}
      \Fee{Arduino (Spark)} {80} {9}
      \Fee{Miscellaneous Arduino Parts} {20} {9}
      \Fee{DHT22 temperature-humidity sensor} {10} {5}
      \Fee{Spark Power Outlet, Sensors, and Controllers} {60} {10}
      \Fee{PC Casing} {120} {1}
      \Fee{PC Motherboard} {160} {1}
      \Fee{PC Radeon Graphics Processor} {200} {1}
      \Fee{PC 600-750 W Power Supply (price for 850W)} {140} {1}
      \Fee{PC FX Central Processor} {200} {1}
      \Fee{PC 250GB Solid State Drive} {150} {1}
      \Fee{PC 8GB RAM} {80} {1}
      \Fee{PC Cooling Units} {50} {1}
      \Fee{Unknown Expenses in Description} {1} {1000}
    \end{invoice}
    
    \closing{Thanks,}
  \end{letter}
\end{document}